---
title: "individual2"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## 1

The mean of the ratings is 3.18

The boxplot shows the average being around 3.25

The histogram shows an average being a little more than 3

There are outliers between 1 and 2

This shows that most ratings are around the 3.1 to 3.5 range which is around "Recommended" and "Highly Recommended" on the scale

There are very few that are rated low around 1 to 2

```{r, echo=FALSE}
#*(1)
choco <- read.csv("https://raw.githubusercontent.com/xdaiISU/ds202materials/master/hwlabs/data/choco.csv") 
library(ggplot2)

ratings <- choco$Rating
boxplot(ratings)
hist(ratings)
paste(c("Mean of ratings = ",mean(ratings)), sep = '')
```

## 2

The most ratings were done in the year 2015

The number of ratings increased from 2006 to 2015 then started to decline

```{r, echo=FALSE}
#*(2)
choco <- read.csv("https://raw.githubusercontent.com/xdaiISU/ds202materials/master/hwlabs/data/choco.csv") 
library(ggplot2)
numOfReports <- data.frame(table(choco$Date))
barplot(numOfReports$Freq, names.arg = numOfReports$Var1)

```

## 3

There does not seem to be any correlation between cacao percentage and the rating of the chocolate bar

We can see that almost all ratings have a chocolate that has high cocoa percentage

There is no clear distinction of any trend lines in this scatter plot

```{r, echo=FALSE}
#*(3)
choco <- read.csv("https://raw.githubusercontent.com/xdaiISU/ds202materials/master/hwlabs/data/choco.csv") 
library(ggplot2)
cacaoAndRatings <- data.frame(choco$Rating, choco$Cocoa_Percent)
plot(cacaoAndRatings)

```

## 4

I separated the ratings into their respective categories (1 - 1.9, 2 - 2.9, 3 - 3.49, etc.), took the top rated, and took the top 5 that occurred most often

Creamy is the most common in the 4 - 5 rating

Creamy is most common in the 3.5 - 4 rating

Sandy is most common in the 3 - 3.49 rating

Sandy is most common in the 2 - 2.9 rating

We can say that top rating chocolates usually have Creamy as their first characteristic

```{r, echo=FALSE}
#*(4)
choco <- read.csv("https://raw.githubusercontent.com/xdaiISU/ds202materials/master/hwlabs/data/choco.csv") 
library(ggplot2)
char1AndRatings <- data.frame(choco$Characteristics1, choco$Rating)
a <- char1AndRatings[char1AndRatings$choco.Rating >= 4,]
b <- char1AndRatings[char1AndRatings$choco.Rating >= 3.5 & char1AndRatings$choco.Rating <= 3.9,]
c <- char1AndRatings[char1AndRatings$choco.Rating >= 3 & char1AndRatings$choco.Rating <= 3.49,]
d <- char1AndRatings[char1AndRatings$choco.Rating >= 2 & char1AndRatings$choco.Rating < 2.9,]
e <- char1AndRatings[char1AndRatings$choco.Rating >= 1 & char1AndRatings$choco.Rating <= 1.9,]

aT <- data.frame(table(a))
bT <- data.frame(table(b))
cT <- data.frame(table(c))
dT <- data.frame(table(d))
eT <- data.frame(table(e))

aTop <- aT[order(aT$choco.Rating, decreasing = TRUE),]
aTopR <- aT[aT$choco.Rating == aTop$choco.Rating[1],]
aTopR <- aTopR[order(aTopR$Freq, decreasing = TRUE),]
aTop5 <- aTopR[1:5,]
aTop5

bTop <- bT[order(bT$choco.Rating, decreasing = TRUE),]
bTopR <- bT[bT$choco.Rating == bTop$choco.Rating[1],]
bTopR <- bTopR[order(bTopR$Freq, decreasing = TRUE),]
bTop5 <- bTopR[1:5,]
bTop5

cTop <- cT[order(cT$choco.Rating, decreasing = TRUE),]
cTopR <- cT[cT$choco.Rating == cTop$choco.Rating[1],]
cTopR <- cTopR[order(cTopR$Freq, decreasing = TRUE),]
cTop5 <- cTopR[1:5,]
cTop5

dTop <- dT[order(dT$choco.Rating, decreasing = TRUE),]
dTopR <- dT[dT$choco.Rating == dTop$choco.Rating[1],]
dTopR <- dTopR[order(dTopR$Freq, decreasing = TRUE),]
dTop5 <- dTopR[1:5,]
dTop5

eTop <- eT[order(eT$choco.Rating, decreasing = TRUE),]
eTopR <- eT[eT$choco.Rating == eTop$choco.Rating[1],]
eTopR <- eTopR[order(eTopR$Freq, decreasing = TRUE),]
eTop5 <- eTopR[1:5,]
eTop5

barplot(aTop5$Freq, names.arg = aTop5$choco.Characteristics1, main='Ratings 4 - 5', ylab='Freq', space = 1.5)
barplot(bTop5$Freq, names.arg = bTop5$choco.Characteristics1, main='Ratings 3.5 - 3.9', ylab='Freq', space = 1.5)
barplot(cTop5$Freq, names.arg = cTop5$choco.Characteristics1, main='Ratings 3 - 3.49', ylab='Freq', space = 1.5)
barplot(dTop5$Freq, names.arg = dTop5$choco.Characteristics1, main='Ratings 2 - 2.9', ylab='Freq', space = 1.5)
barplot(eTop5$Freq, names.arg = eTop5$choco.Characteristics1, main='Ratings 1 - 1.9', ylab='Freq', space = 1.5)
```

## 5

**Bean origin on rating**

I separated the ratings just like in #4

Venezuela is the most common in the 4 - 5 rating

Dominican Republic is most common in the 3.5 - 4 rating

Dominican Republic is most common in the 3 - 3.49 rating

Peru is most common in the 2 - 2.9 rating

The most popular rated chocolate is made from beans from Venezuela with Dominican Republic coming up second

```{r, echo=FALSE}
#*(5.1)
par(mar=c(11,4,4,4))
choco <- read.csv("https://raw.githubusercontent.com/xdaiISU/ds202materials/master/hwlabs/data/choco.csv")
beanOriginAndRatings <- data.frame(choco$Bean_Origin, choco$Rating)
a <- beanOriginAndRatings[beanOriginAndRatings$choco.Rating >= 4,]
b <- beanOriginAndRatings[beanOriginAndRatings$choco.Rating >= 3.5 & beanOriginAndRatings$choco.Rating <= 3.9,]
c <- beanOriginAndRatings[beanOriginAndRatings$choco.Rating >= 3 & beanOriginAndRatings$choco.Rating <= 3.49,]
d <- beanOriginAndRatings[beanOriginAndRatings$choco.Rating >= 2 & beanOriginAndRatings$choco.Rating < 2.9,]
e <- beanOriginAndRatings[beanOriginAndRatings$choco.Rating >= 1 & beanOriginAndRatings$choco.Rating <= 1.9,]

aT <- data.frame(table(a))
bT <- data.frame(table(b))
cT <- data.frame(table(c))
dT <- data.frame(table(d))
eT <- data.frame(table(e))

aTop <- aT[order(aT$choco.Rating, decreasing = TRUE),]
aTopR <- aT[aT$choco.Rating == aTop$choco.Rating[1],]
aTopR <- aTopR[order(aTopR$Freq, decreasing = TRUE),]
aTop5 <- aTopR[1:5,]
aTop5

bTop <- bT[order(bT$choco.Rating, decreasing = TRUE),]
bTopR <- bT[bT$choco.Rating == bTop$choco.Rating[1],]
bTopR <- bTopR[order(bTopR$Freq, decreasing = TRUE),]
bTop5 <- bTopR[1:5,]
bTop5

cTop <- cT[order(cT$choco.Rating, decreasing = TRUE),]
cTopR <- cT[cT$choco.Rating == cTop$choco.Rating[1],]
cTopR <- cTopR[order(cTopR$Freq, decreasing = TRUE),]
cTop5 <- cTopR[1:5,]
cTop5

dTop <- dT[order(dT$choco.Rating, decreasing = TRUE),]
dTopR <- dT[dT$choco.Rating == dTop$choco.Rating[1],]
dTopR <- dTopR[order(dTopR$Freq, decreasing = TRUE),]
dTop5 <- dTopR[1:5,]
dTop5

eTop <- eT[order(eT$choco.Rating, decreasing = TRUE),]
eTopR <- eT[eT$choco.Rating == eTop$choco.Rating[1],]
eTopR <- eTopR[order(eTopR$Freq, decreasing = TRUE),]
eTop5 <- eTopR[1:5,]
eTop5

barplot(aTop5$Freq, names.arg = aTop5$choco.Bean_Origin, main='Ratings 4 - 5', ylab='Freq', space = 1.5, las=2, cex.names = 0.8)
barplot(bTop5$Freq, names.arg = bTop5$choco.Bean_Origin, main='Ratings 3.5 - 3.9', ylab='Freq', space = 1.5, las=2, cex.names = 0.8)
barplot(cTop5$Freq, names.arg = cTop5$choco.Bean_Origin, main='Ratings 3 - 3.49', ylab='Freq', space = 1.5, las=2, cex.names = 0.8)
barplot(dTop5$Freq, names.arg = dTop5$choco.Bean_Origin, main='Ratings 2 - 2.9', ylab='Freq', space = 1.5, las=2, cex.names = 0.8)
barplot(eTop5$Freq, names.arg = eTop5$choco.Bean_Origin, main='Ratings 1 - 1.9', ylab='Freq', space = 1.5, las=2, cex.names = 0.8)
```

**Company on rating**

I separated the ratings just like in #4

Soma is the most common in the 4 - 5 rating

Soma is most common in the 3.5 - 4 rating

Soma is most common in the 3 - 3.49 rating

Hotel Chocolat (Coppeneur) is most common in the 2 - 2.9 rating

The most popular rated chocolate is made by Soma

But Soma also makes some mediocre chocolate as well

```{r, echo=FALSE}
#*(5.2)
par(mar=c(11,4,4,4))
choco <- read.csv("https://raw.githubusercontent.com/xdaiISU/ds202materials/master/hwlabs/data/choco.csv") 
companyAndRatings <- data.frame(choco$Company, choco$Rating)
a <- companyAndRatings[companyAndRatings$choco.Rating >= 4,]
b <- companyAndRatings[companyAndRatings$choco.Rating >= 3.5 & companyAndRatings$choco.Rating <= 3.9,]
c <- companyAndRatings[companyAndRatings$choco.Rating >= 3 & companyAndRatings$choco.Rating <= 3.49,]
d <- companyAndRatings[companyAndRatings$choco.Rating >= 2 & companyAndRatings$choco.Rating < 2.9,]
e <- companyAndRatings[companyAndRatings$choco.Rating >= 1 & companyAndRatings$choco.Rating <= 1.9,]

aT <- data.frame(table(a))
bT <- data.frame(table(b))
cT <- data.frame(table(c))
dT <- data.frame(table(d))
eT <- data.frame(table(e))

aTop <- aT[order(aT$choco.Rating, decreasing = TRUE),]
aTopR <- aT[aT$choco.Rating == aTop$choco.Rating[1],]
aTopR <- aTopR[order(aTopR$Freq, decreasing = TRUE),]
aTop5 <- aTopR[1:5,]
aTop5

bTop <- bT[order(bT$choco.Rating, decreasing = TRUE),]
bTopR <- bT[bT$choco.Rating == bTop$choco.Rating[1],]
bTopR <- bTopR[order(bTopR$Freq, decreasing = TRUE),]
bTop5 <- bTopR[1:5,]
bTop5

cTop <- cT[order(cT$choco.Rating, decreasing = TRUE),]
cTopR <- cT[cT$choco.Rating == cTop$choco.Rating[1],]
cTopR <- cTopR[order(cTopR$Freq, decreasing = TRUE),]
cTop5 <- cTopR[1:5,]
cTop5

dTop <- dT[order(dT$choco.Rating, decreasing = TRUE),]
dTopR <- dT[dT$choco.Rating == dTop$choco.Rating[1],]
dTopR <- dTopR[order(dTopR$Freq, decreasing = TRUE),]
dTop5 <- dTopR[1:5,]
dTop5

eTop <- eT[order(eT$choco.Rating, decreasing = TRUE),]
eTopR <- eT[eT$choco.Rating == eTop$choco.Rating[1],]
eTopR <- eTopR[order(eTopR$Freq, decreasing = TRUE),]
eTop5 <- eTopR[1:5,]
eTop5

barplot(aTop5$Freq, names.arg = aTop5$choco.Company, main='Ratings 4 - 5', ylab='Freq', space = 1.5, las=2, cex.names = 0.8)
barplot(bTop5$Freq, names.arg = bTop5$choco.Company, main='Ratings 3.5 - 3.9', ylab='Freq', space = 1.5, las=2, cex.names = 0.8)
barplot(cTop5$Freq, names.arg = cTop5$choco.Company, main='Ratings 3 - 3.49', ylab='Freq', space = 1.5, las=2, cex.names = 0.8)
barplot(dTop5$Freq, names.arg = dTop5$choco.Company, main='Ratings 2 - 2.9', ylab='Freq', space = 1.5, las=2, cex.names = 0.8)
barplot(eTop5$Freq, names.arg = eTop5$choco.Company, main='Ratings 1 - 1.9', ylab='Freq', space = 1.5, las=2, cex.names = 0.8)
```

