---
title: "Collaboration Document"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Binaya Shrestha
**Company on rating**

I separated the ratings just like in #4

Soma is the most common in the 4 - 5 rating

Soma is most common in the 3.5 - 4 rating

Soma is most common in the 3 - 3.49 rating

Hotel Chocolat (Coppeneur) is most common in the 2 - 2.9 rating

The most popular rated chocolate is made by Soma

But Soma also makes some mediocre chocolate as well

```{r, echo=FALSE}
#*(5.2)
par(mar=c(11,4,4,4))
choco <- read.csv("https://raw.githubusercontent.com/xdaiISU/ds202materials/master/hwlabs/data/choco.csv") 
companyAndRatings <- data.frame(choco$Company, choco$Rating)
a <- companyAndRatings[companyAndRatings$choco.Rating >= 4,]
b <- companyAndRatings[companyAndRatings$choco.Rating >= 3.5 & companyAndRatings$choco.Rating <= 3.9,]
c <- companyAndRatings[companyAndRatings$choco.Rating >= 3 & companyAndRatings$choco.Rating <= 3.49,]
d <- companyAndRatings[companyAndRatings$choco.Rating >= 2 & companyAndRatings$choco.Rating < 2.9,]
e <- companyAndRatings[companyAndRatings$choco.Rating >= 1 & companyAndRatings$choco.Rating <= 1.9,]

aT <- data.frame(table(a))
bT <- data.frame(table(b))
cT <- data.frame(table(c))
dT <- data.frame(table(d))
eT <- data.frame(table(e))

aTop <- aT[order(aT$choco.Rating, decreasing = TRUE),]
aTopR <- aT[aT$choco.Rating == aTop$choco.Rating[1],]
aTopR <- aTopR[order(aTopR$Freq, decreasing = TRUE),]
aTop5 <- aTopR[1:5,]
aTop5

bTop <- bT[order(bT$choco.Rating, decreasing = TRUE),]
bTopR <- bT[bT$choco.Rating == bTop$choco.Rating[1],]
bTopR <- bTopR[order(bTopR$Freq, decreasing = TRUE),]
bTop5 <- bTopR[1:5,]
bTop5

cTop <- cT[order(cT$choco.Rating, decreasing = TRUE),]
cTopR <- cT[cT$choco.Rating == cTop$choco.Rating[1],]
cTopR <- cTopR[order(cTopR$Freq, decreasing = TRUE),]
cTop5 <- cTopR[1:5,]
cTop5

dTop <- dT[order(dT$choco.Rating, decreasing = TRUE),]
dTopR <- dT[dT$choco.Rating == dTop$choco.Rating[1],]
dTopR <- dTopR[order(dTopR$Freq, decreasing = TRUE),]
dTop5 <- dTopR[1:5,]
dTop5

eTop <- eT[order(eT$choco.Rating, decreasing = TRUE),]
eTopR <- eT[eT$choco.Rating == eTop$choco.Rating[1],]
eTopR <- eTopR[order(eTopR$Freq, decreasing = TRUE),]
eTop5 <- eTopR[1:5,]
eTop5

barplot(aTop5$Freq, names.arg = aTop5$choco.Company, main='Ratings 4 - 5', ylab='Freq', space = 1.5, las=2, cex.names = 0.8)
barplot(bTop5$Freq, names.arg = bTop5$choco.Company, main='Ratings 3.5 - 3.9', ylab='Freq', space = 1.5, las=2, cex.names = 0.8)
barplot(cTop5$Freq, names.arg = cTop5$choco.Company, main='Ratings 3 - 3.49', ylab='Freq', space = 1.5, las=2, cex.names = 0.8)
barplot(dTop5$Freq, names.arg = dTop5$choco.Company, main='Ratings 2 - 2.9', ylab='Freq', space = 1.5, las=2, cex.names = 0.8)
barplot(eTop5$Freq, names.arg = eTop5$choco.Company, main='Ratings 1 - 1.9', ylab='Freq', space = 1.5, las=2, cex.names = 0.8)
```

## Jack Langenwalter
## Rating by Bean origin
## Data shows the worst average ratings for Cocoa Beans are for the beans from Martinique(2.75), Principe(2.75), Puerto Rico(2.75), St. Vincent-Grenadines(2.75), and Ivory Coast(2.80)
## While the highest rated beans come from Tobago(3.63). Followed by Sao Tome & Principe(3.5), Solomon Islands(3.45), Congo(3.32), and Thailand(3.30)
```{r}
choco <- read.csv("https://raw.githubusercontent.com/xdaiISU/ds202materials/master/hwlabs/data/choco.csv")
str(choco)
```

```{r}
library(ggplot2)
library(Hmisc)
averages<-aggregate(Rating ~ Bean_Origin, choco, mean) 
newdata<- averages[order(averages$Rating),]
head(newdata)
tail(newdata)
```

